rotation_runs2020_sam v1

### 2020-01-10 inst/documents/rotation_runs2019.Rmd
edit runs files

# to move the pdf of a preceeding run of this file to a saved location
# RUN the line above and below after knitting the file
# ASSUMING id_expt still set to previous run and still same day
# BEWARE that id_expt will not be set correctly in home env if file was knitted
#file.rename("rotation_runs2019.pdf",paste0(outFolder,format(Sys.time(), "%Y-%m-%d-"),id_expt,"-results-figs.pdf"))

>>>>

# to move the pdf of a preceeding run of this file to a saved location
# RUN the line above and below after knitting the file
# ASSUMING id_expt still set to previous run and still same day
# BEWARE that id_expt will not be set correctly in home env if file was knitted
file.rename("rotation_runs2019.pdf",paste0(outFolder,format(Sys.time(), "%Y-%m-%d-"),id_expt,"-results-figs.pdf"))

### 2020-01-10 inst/documents/rotation_runs2020_sam.rmd
edit runs files

---
title: "rotation_runs2020_sam"
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

#Sam: Andy, it appears that TinyTex is also required 
library(tinytex)
outFolder <- "I:/Rotations/Results_Jan/"
```

>>>>

---
title: "rotation_runs2020_sam v1"
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

#Sam: Andy, it appears that TinyTex is also required 
library(tinytex)
outFolder <- "I:/Rotations/Results_Jan/"
#outFolder <- "C:\\Dropbox\\resistanceResults\\rotations\\"
```
